\documentclass{article}
\usepackage{authblk}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{braket}
\usepackage{algorithm}
\usepackage{algpseudocode}
\newcommand{\sgn}{\operatorname{sgn}}
\DeclareMathOperator*{\E}{\mathbb{E}}
\DeclareMathOperator*{\spn}{\operatorname{span}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\algorithmautorefname}{Algorithm}
\usepackage{cite,color,float}
\usepackage[utf8]{inputenc}
\usepackage{tabularx}

\newcommand{\KM}[1]{{\footnotesize\color{cyan}[KM: #1]}}
\newcommand{\Ethan}[1]{{\footnotesize\color{magenta}[Ethan: #1]}}
\newcommand{\Miriam}[1]{{\footnotesize\color{blue}[Miriam: #1]}}

\title{QMPC-constant-round}
\author[1]{Hao Chung}
\author[2]{Kai-Min Chung}
\author[3]{Mi-Ying Huang}
\author[4]{Yi Lee}
\author[5]{Yu-Ching Shen}
\affil[1, 2, 3, 4, 5]{Institute of Information Science, Academia Sinica, Taiwan}
\affil[1, 3, 5]{Department of Computer Science, National Taiwan University, Taiwan}
\affil[4]{Department of Physics, National Taiwan University, Taiwan}

\input{macros}

\begin{document}

\maketitle

\begin{abstract}
	identifiable sending
\end{abstract}

\begin{algorithm}
	\caption{The protocol for checking...}
	\label{AlgGroundStateCheck}
	\begin{algorithmic}[1]
		\State Alice creates a QECC $(\rho_i)$ tolerating $|E|$ errors
		\State Create a componete graph $G$ with each vertex corresponding to a player
		\For{$i\gets 1, N$}
			\State Choose and agree on a shortest path from Alice to Bob
			\If{Path not found}
				\State Abort
				\State Relays connected with Alice accuse Bob
				\State Other relays accuse Bob
			\EndIf
		\EndFor
		\State send $\rho_i$ along the path
		\If{dropped}
			\State Remove from $G$ the edge where dropped
		\EndIf
	\end{algorithmic}
\end{algorithm}

\begin{thm}
	Let $G=(V,E)$ be a connected graph. Remove an edge $(v_1, v_2)$ from it and create $G'=(V,E\setminus\set{(v_1, v_2)}$. One of the following is true:
	\begin{enumerate}
	\item $G'$ is connected
	\item $G'$ has two connected components, one containing $v_1$ and the other containing $v_2$
	\end{enumerate}
\end{thm}
\begin{proof}
The first case is obvious. So assume case 1 isn't true.

Then $G'$ has at most two connected components, since an edge connects two vertices and therefore putting it back wouldn't be able to rejoin three or more connected components.

Define the following sets
$$C_1=\set{v|v\in G', v \textnormal{ is connected to } v_1}$$
$$C_2=\set{v|v\in G', v \textnormal{ isn't connected to } v_1}$$

It's clear that $C_1\cap C_2=V$.

Let $v\in C_2$. Then consider the path from $v$ to $v_1$ in $G$. It must've been broken through the removal of $(v_1, v_2)$, so the path must've crossed through said edge.
Take the partial path with that last edge removed and we see that $v$ is connected with $v_2$.

So all vertices in $C_2$ is connected to $v_2$, so $C_2$ forms a connected component that contains $v_2$.
\end{proof}
\begin{cor}
Define $G$ and $G'$ as above.

Let $A, B\in V$, and let $(v_1, v_2)$ be on an acyclic path from $A$ to $B$ in $G$.

Then in case 2, the connected component containing $v_1$ must also contain $A$, and vise versa with $v_2$ and $B$.
\end{cor}
\begin{proof}
Consider the partial paths from $A$ to $B$ with $(v_1, v_2)$ removed.
\end{proof}

\begin{thm}
\Ethan{TODO ref} The protocol above is correct

Completeness: If Alice and Bob are both honest, the shortest path is the one between them and the algorithm will not abort.

Soundness:
According to corollary above, if the algorithm aborts, then the last edge removed must've broken the graph into two connected components.

All honest relays must be on the same connected component, since edges will not be broken between them, so they must accuse the same party.
Their accusation will be correct since the edge directly connecting to each honest party and the one they accuse have been removed, meaning who they accuse must've dropped a message.

\end{thm}


\end{document}
